Memory for television episodes preserves event content while introducing new across-event similarities

### 2020-02-01 paper/main.tex
updated brain fig, added neurosynth fig, added placeins package for floatbarrier command
recompiled paper, started new figure caption

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{geometry}
\usepackage{natbib}
\usepackage{pxfonts}
\usepackage{graphicx}
\usepackage{newfloat}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{lineno}

@@

@@

\begin{figure}[tp]
\centering
\includegraphics[width=1\textwidth]{figs/brains_panels}
\caption{\small \textbf{Brain structures that underlie the transformation of experience into memory.} \textbf{A.} We searched for regions whose responses (as participants watched the video) matched the temporal correlation matrix of the video topic proportions.  These regions are sensitive to the narrative structure of the video.  \textbf{B.} We searched for regions whose responses (as participants watched the video) matched the temporal correlation matrix of the topic proportions derived from each individual's later recall of video.  These regions are sensitive to how the narrative structure of the video is transformed into a memory of the video.  Both panels: the maps are thresholded at $p < 0.05$, corrected.}
\label{fig:brainz}
\end{figure}

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{geometry}
\usepackage{natbib}
\usepackage{pxfonts}
\usepackage{graphicx}
\usepackage{newfloat}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{lineno}
\usepackage{placeins}

@@

\begin{figure}[tp]
  \centering
  \includegraphics[width=1\textwidth]{figs/precision_detail}
  \caption{\small \textbf{Precision metric reflects quality and specificity of recall.} \textbf{A.} Recall precision distributions over participants, for each video event.  Grey violin plots display kernel density estimates for the distribution of recall precision scores for a single video event.  Colored dots within the violin plots represent each participant's recall precision for that event.  Video events are ordered along the $x$-axis by the average precision with which they were remembered.  \textbf{B.} The set of text annotatations (generated by \citealp{ChenEtal17}) comprising 
   \textbf{C.} }
  \label{fig:precision-detail}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=1\textwidth]{figs/searchlights}
\caption{\small \textbf{Brain structures that underlie the transformation of experience into memory.} \textbf{A.} We searched for regions whose responses (as participants watched the video) matched the temporal correlation matrix of the video topic proportions.  These regions are sensitive to the narrative structure of the video.  \textbf{B.} We searched for regions whose responses (as participants watched the video) matched the temporal correlation matrix of the topic proportions derived from each individual's later recall of video.  These regions are sensitive to how the narrative structure of the video is transformed into a memory of the video.  Both panels: the maps are thresholded at $p < 0.05$, corrected.}
\label{fig:brainz}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=1\textwidth]{figs/neurosynth_decoding}
\caption{\small \textbf{INSERT CAPTION HERE}}
\label{fig:brainz}
\end{figure}
\FloatBarrier
